\chapter{References}

\begin{enumerate}
    \item Burg, J.; Chen, K.; Singh, R.; Venable, M. \textit{Evaluating the Use of LLMs for Automated DOM-Level Resolution of Web Performance Issues.} Proceedings of the 23rd International Conference on Mining Software Repositories (MSR), IEEE/ACM, 2026. (To appear)
    
    \item Ghattas, M.; Mora, A.M.; Odeh, S. \textit{A Novel Approach for Evaluating Web Page Performance Based on Machine Learning Algorithms and Optimization Algorithms.} AI, 2025.
    
    \item Goldwasser, J.; Hooker, G. \textit{Provably Stable Feature Rankings with SHAP and LIME.} Preprint at arXiv:2401.15800, 2024.
    
    \item van Riet, J.; Malavolta, I.; Ghaleb, T.A. \textit{Optimize along the way: An industrial case study on web performance.} J. Syst. Softw., vol. 198, 2023.
    
    \item Salih, A.M. et al. \textit{A Perspective on Explainable Artificial Intelligence Methods: SHAP and LIME.} Adv. Intell. Syst., 2024.
    
    \item Sehwag, A. et al. \textit{Applying Predictive Prefetching Using Deep Learning and NLP to Shorten Web Page Loading Times.} Int. J. Multidiscip. Res. (IJFMR), 2024.
    
    \item Mathur, S.; Bhattacharjee, S.; Hasan, Y.; Rana, A. \textit{Artificial Intelligence Based Predictive Analytics for Website Performance Optimization.} Proceedings of the 7th International Conference on Contemporary Computing and Informatics (IC3I), 2024, pp. 795-800.

    \item Kaushik, N.; Kumar, H.; Raj, V. \textit{Micro Frontend Based Performance Improvement and Prediction for Microservices Using Machine Learning.} J. Grid Comput., vol. 22, 2024.
    
    \item Yang, X. et al. \textit{Machine learning-driven clinical decision support for low bone mineral density: A web-based prediction model with explainable AI integration.} Bone, vol. 200, 2025.

    \item Dakić, V.; Đambić, G.; Slovinac, J.; Redžepagić, J. \textit{Optimizing Kubernetes Scheduling for Web Applications Using Machine Learning.} Electronics, vol. 14, no. 5, 2025.
    
    \item Huang, D.; Costero, L.; Pahlevan, A.; Zapater, M.; Alonso, D. \textit{Cloud Prophet: A Machine Learning-Based Performance Prediction for Public Clouds.} IEEE Trans. Sustain. Comput., 2023.
    
    \item Xin, R.; Liu, H.; Chen, P.; Zhao, Z. \textit{Robust and accurate performance anomaly detection and prediction for cloud applications: a novel ensemble learning-based framework.} J. Cloud Comput., vol. 12, 2023.
    
    \item Notz, P.M.; Pibernik, R. \textit{Explainable subgradient tree boosting for prescriptive analytics in operations management.} Eur. J. Oper. Res., vol. 312, no. 3, pp. 1119-1133, 2024.
    
    \item Asha, M.M.; Ramya, G. \textit{Predator crow search optimization with explainable AI for cardiac vascular disease classification.} Sci. Rep., vol. 15, 2025.
    
    \item Goścień, R. \textit{Explainable artificial intelligence-based framework for efficient content placement in elastic optical networks.} Expert Syst. Appl., vol. 262, 2025.
    
    \item Surianarayanan, C.; Lawrence, J.J.; Chelliah, P.R.; Prakash, E.; Hewage, C. \textit{A Survey on Optimization Techniques for Edge Artificial Intelligence (AI).} Sensors, vol. 23, no. 3, 2023.
    
    \item Liu, B.; Vu-Bac, N.; Zhuang, X.; Lu, W.; Fu, X.; Rabczuk, T. \textit{AI-DeMat: A web-based expert system platform for computationally expensive models in materials design.} Adv. Eng. Softw., vol. 176, 2023.
    
    \item Hassija, V. et al. \textit{Interpreting Black-Box Models: A Review on Explainable Artificial Intelligence.} Cogn. Comput., vol. 16, pp. 45-74, 2024.
    
    \item Mersha, M.; Lam, K.N.; Wood, J.; AlShami, A.; Kalita, J. \textit{Explainable artificial intelligence: A survey of needs, techniques, applications, and future direction.} Neurocomputing, vol. 599, 2024.
    
    \item Bennetot, A. et al. \textit{A Practical Tutorial on Explainable AI Techniques.} ACM Comput. Surv., vol. 57, 2024.
    
    \item Ortigossa, E.; Gonçalves, T.; Nonato, L. \textit{Explainable Artificial Intelligence (XAI) - From Theory to Methods and Applications.} IEEE Access, vol. 12, pp. 80799-80846, 2024.
    
    \item Ali, S. et al. \textit{Explainable Artificial Intelligence (XAI): What we know and what is left to attain Trustworthy Artificial Intelligence.} Inf. Fusion, vol. 99, 2023.
    
    \item Hosain, M.; Jim, J.; Mridha, M.; Kabir, M. \textit{Explainable AI approaches in deep learning: Advancements, applications and challenges.} Comput. Electr. Eng., vol. 117, 2024.
    
    \item Zhou, N. et al. \textit{Explainable AI Frameworks: Navigating the Present Challenges and Unveiling Innovative Applications.} Algorithms, vol. 17, no. 6, 2024.
    
    \item Mersha, M.; Yigezu, M.; Tonja, A.; Shakil, H.; Iskandar, S.; Kolesnikova, O.; Kalita, J. \textit{Explainable AI: XAI-guided context-aware data augmentation.} Expert Syst. Appl., vol. 289, 2025.
    
    \item Alam, K.; Kifayat, K.; Sampedro, G.A.; Karovic, V.; Naeem, T. \textit{SXAD: Shapely eXplainable AI-Based Anomaly Detection Using Log Data.} IEEE Access, vol. 12, pp. 95659-95672, 2024.
    
    \item Rahim, N.; Basheer, K.P. \textit{A Hybrid Explainability Framework for Recommender Systems Using SHAP with Natural Language Interpretations.} Int. J. Innov. Res. Sci. Stud., vol. 8, no. 6, pp. 687-703, 2025.
    
    \item Benleulmi, M.; Gasmi, I.; Azizi, N.; Dey, N. \textit{Explainable AI and Deep Learning Models for Recommender Systems: State of the Art and Challenges.} J. Univers. Comput. Sci., vol. 31, no. 4, pp. 383-421, 2025.
    
    \item Goyal, B. \textit{Explainable AI (XAI) for Cloud-Based Enterprise Applications: Building Trust and Transparency in AI-Driven Decisions.} J. Int. Crisis Risk Commun. Res., vol. 8, no. S9, pp. 63-71, 2025.
    
    \item Bhardwaj, T.; Sumangali, K. \textit{An explainable federated blockchain framework with privacy-preserving AI optimization for securing healthcare data.} Sci. Rep., vol. 15, 2025.
\end{enumerate}